Analysis of split plot design using MCMCglmm

### 2020-07-08 README.Rmd
Correct repository names to sync with Dockerhub

The files at the URL above will generate the results as found in the publication.
The files hosted at <https://github.com/adamhsparks/rice_awd_shb> are the development versions and may have changed since the report was published.

@@

```
git clone https://github.com/adamhsparks/rice_awd_shb.git
```

>>>>

The files at the URL above will generate the results as found in the publication.
The files hosted at <https://github.com/adamhsparks/rice-awd-shb> are the development versions and may have changed since the report was published.

@@

```
git clone https://github.com/adamhsparks/rice-awd-shb.git
```
